Spin canonical divisors of log stacky curves

### 2015-06-28 stacky_write_up/spin_cring.tex
address all g0 todos, rewrite g0 transitions, table

\begin{lem}
\label{lem:sat-3}
\todo{Make explicit assumptions on genus.}
Suppose $L'$ is a log half-canonical divisor of $\sx'$ with course
space $X$ of genus 0 such that $\sat(\Eff(\halfcan')) = 3$ and $R_
{\halfcan'} = k[x_3, x_4 , x_5, \ldots, x_m]/I'$. Let $L = L' + \frac
{1}{3}P$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that
the ordering on $k[x]$ satisfies
\begin{align*}
	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
\end{align*}

@@

\ssec{Saturation}
\label{ssec:g_0_saturation}
First, we present the saturations of the canonical divisor for
all cases where $g = 0$ and $\delta = 0,$ as defined in Definition
~\ref{defn:sat}. The saturation can be computed via applications
of Riemann-Roch. Exceptional cases are listed
first and generic cases follow.

@@

\todo{transition}
Here we describe induction of raising degrees from Lemma ~\ref{lem:raise-stacky-order}

\ssec{Base Cases}
\label{ssec:g_0_base}
Now we have an inductive statement on the number of stacky
points in Lemma ~\ref{lem:sat-3} and
an inductive statement on stabilizer orders in Theorem
~\ref{lem:raise-stacky-order}. After verifying that explicit triples
$(\sx, L, J)$ of stacky curves $\sx$ with particular signatures and
particular choices of $J$ are admissible, we will use Lemmas ~\ref{lem:raise-stacky-order}, and ~\ref{lem:sat-3} imply that the spin canonical ring
$R(\sx , 0, L)$ is generated in degree at most $e := \max(5, e_1,
\ldots, e_r)$ with relations generated in degree at most $2e$ for
$\sx$ with any signature $\sigma = (0; e_1, \ldots , e_r; 0)$ outside
of the list of exceptional cases in Table ~\ref{table:g-0-exceptional}.

\begin{lem}
\label{lem:g_0_admissible_cases}
Let $(\sx', \Delta, \halfcan')$ be a log spin curve so that $\sx$ has signature $\sigma = (0; e_1,
\ldots, e_r; 0)$. Then, $R' := R(\sx', \Delta, \halfcan')$ has a
presentation generated as a $k$-algebra by elements of degree at most $e = \max(5
, e_1, \ldots, e_r)$ with relations in degree at most $2e$ and $(\sx
', \halfcan', J) =(\sx
', -\infty + \sum_{i=1}^{r}\subhalf{e_i}P_i, J)$ is admissible for the following cases:

\begin{enumerate}
	\item[(a)] $\sigma_1 = (0; 3, 3, 11; 0), J_1 = \{3\}$
	\item[(b)] $\sigma_2 = (0; 3, 5, 9; 0), J_2 = \{3\}$
	\item[(c)] $\sigma_3 = (0; 3, 7, 7; 0), J_3 = \{2, 3\}$
	\item[(d)] $\sigma_4 = (0; 5, 5, 7; 0), J_4 = \{3\}$
	\item[(e)] $\sigma_5 = (0; 5, 7, 7; 0), J_5 = \{2, 3\}$
	\item[(f)] $\sigma_6 = (0; 7, 7, 7; 0), J_6 = \{1, 2, 3\}$
	\item[(g)] $\sigma_7 = (0; 3, 3, 3, 5; 0), J_7 = \{4\}$
	\item[(h)] $\sigma_8 = (0; 3, 3, 5, 5; 0), J_8 = \{3, 4\}$
	\item[(i)] $\sigma_9 = (0; 3, 5, 5, 5; 0), J_9 = \{2, 3, 4\}$
	\item[(j)] $\sigma_{10} = (0; 5, 5, 5, 5; 0), J_{10} = \{1, 2, 3, 4\}$
	\item[(k)] $\sigma_{11} = (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$
\end{enumerate}

@@

Before proving Lemma ~\ref{lem:g_0_admissible_cases} in general, we check the lemma holds for case (b).

\begin{example}
\label{ex:base-377}
Here we demonstrate, in detail, that case (b) with ($\sigma_2 =
(0; 3, 7, 7; 0), \halfcan' \sim -\infty + \frac{1}{3} P_1 +
\frac{3}{7} P_2 + \frac{3}{7} P_3, J_2 = \{3, 4\},$) with distinct points $P_i \neq \infty$,
satisfies the conditions of Lemma ~\ref{lem:g_0_admissible_cases}.
We exhibit a (minimal) presentation for $R'$.

@@

\noindent
is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
\geq 0$. Since $\sigma_2$ has saturation $s = 5$, as noted in
Table ~\ref{table:g-0-sat}, then this map is surjective
when $d \geq 21 + s = 26$ (i.e. $R'$ is generated up to degree 25).

@@

Also note that $e_j' + 2d = 7 + 2d \nmid 2 = e_i - e_j'$ for all
$i, j \in J_2 = \{2, 3\}$ such that $j \neq i$ and for all $d \geq
0$. Thus, $s_{\sigma_2, J_2}(i, d) = \emptyset$ for each $i \in J$.
Furthermore, $\deg \lfloor e_i \halfcan \rfloor = \deg \lfloor 9
\halfcan \rfloor = 2 \lfloor \frac{4 * 9}{9} \rfloor + \lfloor
\frac{9}{3} \rfloor - 9 = 2$, so (Ad-iii) is satisfied and
$\sigma_2, J_2$ is admissible.

@@

\begin{proof}[Proof of Lemma ~\ref{lem:g_0_admissible_cases}]
For the remaining cases, we can use a similar method to the one
used in Example ~\ref{ex:base-377} to find a presentation the
desired conditions.

The following table demonstrates that $R(\sx', 0, L')$ is
generated as a $k$-algebra by elements of degree at most $e$
with relations in degree at most $2e$ for each case. Also note
that in these cases, $e_i = e + 2 > \deg z$ for all $i \in J$
and any generator $z$ of $R'$.
\begin{longtable}
	{| c || c | c | c |}
	\caption{Genus 0 Non-effective Base Cases Generators/Relations}
	\label{table:g-0-base-cases}

@@

Now we can induct on cases (a)-(k) of Lemma
~\ref{lem:g_0_admissible_cases} to obtain bounds on the minimal
generator and relation degrees for canonical rings of genus 0
curves. This process will be carried out in Subsection
~\ref{ssec:g-0-main}.

\todo{induct on cases?}

@@

It only remains to deal with the case $\delta = 0$, so $\halfcan$ is not effective.
Let $\sigma = (0; e_1, \ldots, e_r; 0)$ be a signature with $r > 0$
so that $\sigma \neq \sigma_i$ where $\sigma_i$ is one of the exceptional cases in Table
~\ref{table:g-0-exceptional}. Note that if $r < 3$, then $\deg 
\lfloor d \halfcan \rfloor < 0$ for all $d \geq 0$ so we have the
trivial case where $R(\sx, \Delta, \halfcan) = k$. Thus, we now
only consider the cases with $r \geq 3$.

If $r > 5$, then we can use Lemma
~\ref{lem:sat-3} to add stacky points with
stabilizer order $3$ to case (k) of Lemma
~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$. This case
clearly satisfies the conditions of Lemma
~\ref{lem:sat-3} (recall from Table ~\ref
{table:g-0-sat} that $\sat(\Eff(\sigma_{11})) = 3$), and the
immediate consequence of parts (a) and (c) of Lemma
~\ref{lem:sat-3} is that any $R(\sx', \Delta,
\halfcan')$ corresponding to signatures $\sigma'$ with ramification
orders all equal to $3$ for any $r > 5$ is generated up to
degree $e := \max(5, e_1', \ldots, e_r')$ with relations generated
up to degree $2e$. Furthermore, these cases satisfy all of the
conditions of Lemma ~\ref{lem:raise-stacky-order}.

So if $r > 5$, then $\sigma$ ``lies above'' the case $(\sigma', J)$
where $\sigma'$ has $r$ many stacky points all of order $3$
and $J = \{1, \ldots, r\}$ in the sense that for all $i
\in J$, $e_i \geq e_i'$ and $e_i = e_i'$ otherwise.
If $r \leq 5$, then $\sigma$ similarly ``lies above'' one of the
base cases of Lemma ~\ref{lem:g_0_admissible_cases}, all of which
satisfy the hypotheses of Lemma ~\ref{lem:raise-stacky-order} as well. \todo{Aaron: I think we replace the above paragraph with an application of Corollary ~\ref{cor:raise-stacky-order}.}

So for any $r > 0$, there is a $(\sigma', J)$, either from
Lemma ~\ref{lem:g_0_admissible_cases} or corresponding to
the $r > 5$ case with stabilizer orders all $3$, with $\sigma' =
(0; e_1', \ldots, e_r'; 0)$ satisfying the property that for all $i
\in J$, $e_i \geq e_i'$ and $e_i = e_i'$ otherwise.

All such base cases satisfy all of the hypotheses of Theorem
~\ref{lem:raise-stacky-order} and their corresponding $R' := R(\sx',
\Delta, \halfcan')$ are generated, as $k$-algebras, up to degree
$e' := \max(5, e_1', \ldots, e_r')$ with relations generated up to
degree $2e'$ by Lemma ~\ref{lem:g_0_admissible_cases}. It follows
from induction using Lemma ~\ref{lem:raise-stacky-order}(b) and
Corollary ~\ref{cor:raise-stacky-order} that $R := R(\sx, \Delta,
\halfcan)$ is generated up to degree $e := \max(5, e_1, \ldots, e_r)$.
It also follows from induction on Lemma ~\ref{lem:raise-stacky-order}(c)
and ~\ref{cor:raise-stacky-order} that the relations are generated
up to degree $2e$. \todo{What does it mean to induct on the statements of two lemmas? Clarify this please.}
 \end{proof}

>>>>

\begin{lem}
\label{lem:sat-3}
\todo{Make explicit assumptions on genus.}
Suppose $L'$ is a log half-canonical divisor of $\sx'$ with coarse
space $X$ of genus 0 such that $\sat(\Eff(\halfcan')) = 3$ and $R_
{\halfcan'} = k[x_3, x_4 , x_5, \ldots, x_m]/I'$. Let $L = L' + \frac
{1}{3}P$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that
the ordering on $k[x]$ satisfies
\begin{align*}
	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
\end{align*}

@@

\ssec{Saturation}
\label{ssec:g_0_saturation}
First, we present the saturations of the canonical divisor for
all cases where $g = 0$ and $\delta = 0,$ as defined in Definition
~\ref{defn:sat}. The saturations can be computed using Riemann-Roch.
By classifying the saturations of all signatures, we can determine
the base cases on which we can apply inductive lemmata from
Section ~\ref{sec:induction}. Exceptional cases are listed first
and generic cases follow.

@@

\ssec{Base Cases}
\label{ssec:g_0_base}
In order to apply Lemma ~\ref{lem:sat-3} and Lemma
~\ref{lem:raise-stacky-order} when $\delta = 0$,
we need to determine appropriate base cases that will
cover all but finitely many signatures by induction.
Here we provide such base cases and demonstrate that
they satisfy all of the necessary conditions of
Lemma ~\ref{lem:sat-3} and Lemma ~\ref{lem:raise-stacky-order}
(e.g. admissibility). We also show that that the associated spin
canonical rings are generated in degree at most $e := \max(5, e_1,
\ldots, e_r)$ with relations generated in degree at most $2e$.

\begin{lem}
\label{lem:g-0-admissible-cases}
Let $(\sx', \Delta, \halfcan')$ be a log spin curve so that $\sx$ has signature $\sigma = (0; e_1,
\ldots, e_r; 0)$. Then, $R' := R(\sx', \Delta, \halfcan')$ has a
presentation generated as a $k$-algebra by elements of degree at most $e = \max(5
, e_1, \ldots, e_r)$ with relations in degree at most $2e$ and $(\sx
', \halfcan', J) =(\sx
', -\infty + \sum_{i=1}^{r}\subhalf{e_i}P_i, J)$ is admissible for the following cases:

\begin{longtable}
	{| c || c | c | c |}
	\caption{Genus 0 Base Cases}
	\label{table:g-0-base-cases}

	\hline
	Case & Signature $\sigma$ & $J$ & $e$\\
	\hline
	\hline

	(a) & (0; 3, 3, 11; 0) & \{3\} & 11\\	\hline

	(b) & (0; 3, 5, 9; 0) & \{3\}	& 9\\ \hline

	(c) & (0; 3, 7, 7; 0) & \{2, 3\}	& 7\\ \hline

	(d) & (0; 5, 5, 7; 0) & \{3\}	& 7\\ \hline

	(e) & (0; 5, 7, 7; 0) & \{2, 3\}	& 7\\ \hline

	(f) & (0; 7, 7, 7; 0) & \{1, 2, 3\}	& 7\\ \hline

	(g) & (0; 3, 3, 3, 5; 0) & \{4\} & 5\\ \hline

	(h) & (0; 3, 3, 5, 5; 0) & \{3, 4\} & 5\\ \hline

	(i) & (0; 3, 5, 5, 5; 0) & \{2, 3, 4\} & 5\\ \hline

	(j) & (0; 5, 5, 5, 5; 0) & \{1, 2, 3, 4\} & 5\\ \hline

	(k) &	(0; 3, 3, 3, 3, 3; 0) & \{1, 2, 3, 4, 5\} & 5\\ \hline
\end{longtable}

@@

Before proving Lemma ~\ref{lem:g-0-admissible-cases} in general, we check the lemma holds for case (b).

\begin{example}
\label{ex:base-377}
Here we demonstrate, in detail, that case (b) with ($\sigma =
(0; 3, 7, 7; 0), \halfcan' \sim -\infty + \frac{1}{3} P_1 +
\frac{3}{7} P_2 + \frac{3}{7} P_3, J = \{3, 4\},$) with distinct points $P_i \neq \infty$,
satisfies the conditions of Lemma ~\ref{lem:g-0-admissible-cases}.
We exhibit a (minimal) presentation for $R'$.

@@

\noindent
is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
\geq 0$. Since $\sigma$ has saturation $s = 5$, as noted in
Table ~\ref{table:g-0-sat}, then this map is surjective
when $d \geq 21 + s = 26$ (i.e. $R'$ is generated up to degree 25).

@@

Also note that $e_j' + 2d = 7 + 2d \nmid 2 = e_i - e_j'$ for all
$i, j \in J = \{2, 3\}$ such that $j \neq i$ and for all $d \geq
0$. Thus, $s_{\sigma, J}(i, d) = \emptyset$ for each $i \in J$.
Furthermore, $\deg \lfloor e_i \halfcan \rfloor = \deg \lfloor 9
\halfcan \rfloor = 2 \lfloor \frac{4 * 9}{9} \rfloor + \lfloor
\frac{9}{3} \rfloor - 9 = 2$, so (Ad-iii) is satisfied and
$\sigma, J$ is admissible.

@@

\begin{proof}[Proof of Lemma ~\ref{lem:g-0-admissible-cases}]
For the remaining cases, we can use a similar method to the one
used in Example ~\ref{ex:base-377} to find a presentation the
desired conditions.

The following table demonstrates that $R(\sx', 0, L')$ is
generated as a $k$-algebra by elements of degree at most $e$
with relations in degree at most $2e$ for each case. Also note
that in these cases, $e_i = e + 2 > \deg z$ for all $i \in J$
and any generator $z$ of $R'$.
\begin{longtable}
	{| c || c | c | c |}
	\caption{Genus 0 Non-effective Base Cases Generators/Relations}
	\label{table:g-0-base-cases-degrees}

@@

Now we can use Lemma ~\ref{lem:sat-3}, Lemma
~\ref{lem:raise-stacky-order}, and Corollary
~\ref{cor:raise-stacky-order} inductively on the cases of Table
~\ref{table:g-0-base-cases} to obtain the desired bounds on the
generator and relation degrees for log spin canonical rings of
genus 0 curves. This process will be carried out in Subsection
~\ref{ssec:g-0-main}.

@@

It only remains to deal with the case $\delta = 0$, so $\halfcan$ is not effective.
Let $\sigma = (0; e_1, \ldots, e_r; 0)$ be a signature with $r > 0$
so that $\sigma$ is not one of the exceptional cases in Table
~\ref{table:g-0-exceptional}. Note that if $r < 3$, then $\deg 
\lfloor d \halfcan \rfloor < 0$ for all $d \geq 0$ so we have the
trivial case where $R(\sx, \Delta, \halfcan) = k$. Thus, we now
only consider the cases with $r \geq 3$.

If $r > 5$, then we can use Lemma
~\ref{lem:sat-3} to add stacky points with
stabilizer order $3$ to case (k) of Table
~\ref{table:g-0-base-cases}, which corresponds to $\sigma
= (0; 3, 3, 3, 3, 3; 0), J = \{1, 2, 3, 4, 5\}$. This case
clearly satisfies the conditions of Lemma
~\ref{lem:sat-3} (recall from Table ~\ref
{table:g-0-sat} that $\sat(\Eff(\sigma)) = 3$), and the
immediate consequence of parts (a) and (c) of Lemma
~\ref{lem:sat-3} is that any $R(\sx', \Delta,
\halfcan')$ corresponding to signatures $\sigma'$ with ramification
orders all equal to $3$ for any $r > 5$ is generated up to
degree $e' := \max(5, e_1', \ldots, e_r')$ with relations generated
up to degree $2e'$. Furthermore, these cases satisfy all of the
conditions of Lemma ~\ref{lem:raise-stacky-order}. Now we can
apply Corollary ~\ref{cor:raise-stacky-order} to deduce that
$R(\sx, \delta, \halfcan)$ is generated up to degree $e :=
\max(5, e_1, \ldots, e_r)$ with relations generated up to degree
$2e$.

If $r \leq 5$ and $\sigma$ is not one of the exceptional cases,
then we may similarly apply Lemma ~\ref{g-0-admissible-cases} and
Corollary ~\ref{cor:raise-stacky-order} to an appropriate base case
from Table ~\ref{table:g-0-base-cases} and deduce that $R(\sx,
\delta, \halfcan)$ is generated up  to degree $e := \max(5, e_1,
\ldots, e_r)$ with relations generated up to degree $2e$.
 \end{proof}
